---
title: "Tutorial2"
author: "Junxiong"
date: "29 January 2016"
output: html_document
---

```{r, message=FALSE,echo=FALSE}
library(ggplot2)

library(dplyr)
```

1ai)
```{r, echo=FALSE}
summarise(labs, avg = mean(WaitTime))
count (labs, SvcSat)
```

1aii)
```{r, echo=FALSE}
ggplot(labs, aes(WaitTime)) + geom_bar()
ggplot(labs, aes(SvcSat)) + geom_bar()
```

1b)
```{r, echo=FALSE}
ggplot(labs, aes(Gender, SvcSat)) + geom_count()
ggplot(labs, aes(AGE, SvcSat)) + geom_count()
```
higher proportion of female is more satisfied than male
people between age 20 to 40 are generally more satisfied with the service 

1c)
```{r, echo=FALSE}
SvcStat <- as.numeric(labs$SvcSat)
ggplot(labs, aes(SvcStat, WaitTime)) + geom_line()
```
The shorter the waiting time, the higher the probability of having a satisfied customer.

1d)
```{r, echo=FALSE}
labs <- mutate(labs, BMI = WT/(HT*HT))
ggplot(labs, aes(TC, BMI)) + geom_point()
```
The points are very spread out, therefore there is minimal correlation between BMI and Total cholestrol

1e)
```{r, echo=FALSE}
labs <- mutate(labs, BMI = WT/(HT*HT))
labs <- arrange(labs, AGE)
labs <- select (labs, ETHNIC, AGE, SBP, TC, BMI) 

```
DO NOT KNOW HOW TO CONTINUE

Page 9
```{r, echo=FALSE}
Diabetics_1 <- mutate (Diabetic, total = Present + Absent)
Diabetics_2 <- mutate (Diabetics_1, Present_Per = Present/total * 100, Absent_Per = Absent/total * 100)
ggplot(Diabetics_2, aes(Diabetic_control, Present_Per)) + geom_bar(stat = "identity")
ggplot(Diabetics_2, aes(Diabetic_control, Absent_Per)) + geom_bar(stat = "identity")
```
a. Yes
b. For good diabetics control, the rate of complications being absent is much higher than poor control. 
c. A larger test group is needed

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
